---
title: "p8105_hw5_yl5215"
author: "Yucheng Li"
date: '2022-11-16'
output: github_document
---

```{r}
library(tidyverse)
```

# Problem 2

```{r}
homicide = 
  read_csv("data/homicide.csv") %>%
  janitor::clean_names()
```
## Decribe the raw data

The dataset contains `r ncol(homicide)` variables and `r nrow(homicide)` observations. The variables included are `r variable.names(homicide)`. `uid` represents case ID which is composed of city name and a number. `victim_last`, `victim_first`, `victim_race`, `victim_age`, `victim_sex` represent the last name, first name, race, age, and sex of the victim, respectively. `city` and `state` represent the city and state where the incident happened, and `lat` and `lon` represent the latitude longitude where the incident happened. `disposition` indicates that the case is either "Closed by arrest", "Closed without arrest", or "Open/No arrest".

## number of homicides and number of unsolved homicides in each city

```{r message=FALSE, warning=FALSE}
homicide = 
  homicide %>% 
  mutate(city_state = paste(city, state, sep = ", ", collapse = NULL))
total_homicide = 
  homicide %>% 
  group_by(city_state) %>% 
  summarize(number_of_homicides = n())
unsolved_homicide = 
  homicide %>%
  filter(disposition != "Closed by arrest") %>% 
  group_by(city_state) %>% 
  summarize(number_of_unsolved_homicides = n())
total_unsolved_homicide = 
  left_join(total_homicide, unsolved_homicide) %>% 
  replace(is.na(.), 0)
total_unsolved_homicide
```

## Proportion of unsolved homicides in Baltimore, MD

```{r message=FALSE, warning=FALSE}
bal_unsolved_prop = 
  prop.test(1825, 2827, p = NULL, 
            alternative = "two.sided", conf.level = 0.95, correct = TRUE)
bal_unsolved_prop
bal_unsolved_prop_tibble = broom::tidy(bal_unsolved_prop)
bal_unsolved_prop_tibble
bal_unsolved_prop_tibble %>% pull(estimate)
bal_unsolved_prop_tibble %>% pull(conf.low)
bal_unsolved_prop_tibble %>% pull(conf.high)
bal_unsolved_prop_tibble %>% mutate(ci = paste("(", round(conf.low, 4), ",", round(conf.high, 4), ")")) %>% pull(ci)
bal_unsolved_prop_tibble
```
## Estimate of the proportion of unsolved homicides and its confidence interval for each city

```{r message=FALSE, warning=FALSE}
unsolved_prop = 
  total_unsolved_homicide %>% 
  filter(city_state != "Tulsa, AL") %>% 
  mutate(result = purrr::map2(.x = number_of_unsolved_homicides, .y = number_of_homicides, ~broom::tidy(prop.test(x = .x, n = .y, alternative = "two.sided", conf.level = 0.95, correct = TRUE)))) %>% 
  unnest(result) %>% 
  select(city_state, estimate, conf.low, conf.high) %>% 
  mutate(confidence_interval = paste("(", round(conf.low, 4), ",", round(conf.high, 4), ")"))

unsolved_prop
```

Data for Tulsa, AL was dropped because it only contains 1 observation and cannot be used to obtain any meaningful inference.

## Plot showing estimates and confidence intervals

```{r}
unsolved_plot = 
  unsolved_prop %>% 
  ggplot(aes(x = reorder(city_state, estimate), y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Estimates and CIs of Proportion of Unsolved Homicides for US Cities", x = "City, State", y = "Estimates")
unsolved_plot
```

